Carcinoma

### 2022-05-15 inst/carcinoma.Rmd
more work on maximum likelihood in carcinoma

To maximize the likelihood we need a good starting point and rather
than use the default `equalp()` we could simply count how many times
each clinician diagnoses carcinoma:

```{r,label=countcarcinoma}
count <- colSums(sweep(carcinoma_table[,1:7],1,carcinoma_table$n,"*"))
names(count) <- colnames(carcinoma_table)[1:7]
count <- count/sum(count)
count
pie(count)
carcinoma_count <- count
```

We can compare this to other reasonable starting points:

```{r,label=calccloglikcount,cache=TRUE}
system.time(lc <- loglik_lsl(count,carcinoma))
```

@@

```{r,label-calcloglikequalp,cache=TRUE}
e <- equalp(W)
system.time(le <- loglik_lsl(e,carcinoma))
```

```{r,label=showthreemethods}
c(count=lc, zipf=lz, equal=le)
```

To find the maximum likelihood estimate we would use:

@@

but this will take many hours (a week?) to run.

@@

```{r,label=savecarcinomadataset}
save(carcinoma_table,carcinoma, carcinoma_count, file="carcinoma.rda")
```

>>>>

There are several natural BT strengths to consider.  First, we could
simply count how many times each clinician diagnoses carcinoma:

```{r,label=countcarcinoma,cache=TRUE}
carcinoma_count <- colSums(sweep(carcinoma_table[,1:7],1,carcinoma_table$n,"*"))
names(carcinoma_count) <- colnames(carcinoma_table)[1:7]
carcinoma_count <- carcinoma_count/sum(carcinoma_count)
carcinoma_count
system.time(lc <- loglik_lsl(carcinoma_count,carcinoma))
```

Secondly, Zipf:

@@

Thirdly, equal probabilities:

```{r,label=calcloglikequalp,cache=TRUE}
e <- equalp(W)
system.time(le <- loglik_lsl(e,carcinoma))
```

The maximum likelihood estimate is somewhat more demanding.  To find
the maximum likelihood estimate we would use:

@@

but this takes many hours to run.  It gives the following:

```{r,label=calculateloglikformaxp, cache=TRUE}
carcinoma_maxp <- 
c(A = 0.118778759012282, B = 0.542873969223425, C = 0.00654044305270073, 
D = 0.00242693714895262, E = 0.202821434317779, F = 0.00130596252816986, 
G = 0.125252494716691)
system.time(lmax <- loglik_lsl(carcinoma_maxp,carcinoma))
```

We are now in a position to compare  these three points:

```{r,label=showthreemethods}
results <- c(count=lc, zipf=lz, equal=le,maxp=lmax)
results <- results - max(results)
results
```

@@

```{r,label=savecarcinomadataset}
save(carcinoma_table,carcinoma, carcinoma_count, carcinoma_maxp,file="carcinoma.rda")
```
